---
title: "Lab 00 - Hello IDS!"
author: "Kumi Stevens"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Carla", "Ash", "Selena", "Shreya" ,"Brogan"),
  github_username = c("cmartin658" ,"ahsbryw7", "selena-314", "ggshreya", "brogan7125"), 
  colour = c("purple", "green4", "pink", 
             "navyblue" , "pink"),
  hobby = c("football", "art", "violin", 
            "cello", "singing"),
  favourite_number = c(9, 7, 7, 2 , 5)
)
team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


This box plot shows the users favourite digit compared to their github username

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "GitHub Username", 
          y = "Favourite umber",
          title = "Box plot that shows Favourite Number compared to GitHub Username, in users favourite colour.")
```

# labs() adds labels to a graph/plot

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

## This plot is bad as there will be too many x variables for it to be readable. To improve this plot, we could split hobbies into sub-categories, such as sports, arts ect. and make people chose the area of their hobby.
